---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HW3

<!-- badges: start -->
[![R-CMD-check](https://github.com/EdwardS2027/HW3/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/EdwardS2027/HW3/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/EdwardS2027/HW3/branch/main/graph/badge.svg)](https://codecov.io/gh/EdwardS2027/HW3?branch=main)
<!-- badges: end -->

## Overview
'HW3' package is created for the purpose of copying the lm() and anova() functions, which can give us the fitted linear regression model and the results of hypothesis testing:
* 'lm2()' fits the linear regression model based on given formula and data, and returns the values similar to ones given from the 'summary()'
* 'anova2()' performs analysis of varaince on the fitted linear regression model for the purpose of hypothesis testing.

## Installation
You should have the 'devtools' package installed, before installing the 'HW3' package. 


``` r
install.packages('devtools')
```
You are now able to install the 'HW3' package by running this command
``` r
devtools::install_github("EdwardS2027/HW3", build_vignettes = T)
```

To access this package, run
``` r
library("HW3")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library("HW3")
# Peeking at the sample dataset
head(melb_data)

# Looking at the coefficents generated by lm2
coeff = lm2(melb_data$Price~melb_data$YearBuilt+melb_data$Car+melb_data$Landsize,melb_data,na.action="omit")$coefficients
coeff
#>                         Estimate   Std. Error    t value      Pr(>|t|)
#>(Intercept)          1.321950e+07 3.513085e+05  37.629333 6.385300e-286
#>melb_data$YearBuilt -6.363473e+03 1.792960e+02 -35.491433 9.927155e-257
#>melb_data$Car        2.083608e+05 7.139330e+03  29.184915 3.312875e-178
#>melb_data$Landsize   3.487448e+01 6.725109e+00   5.185712  2.203520e-07

# Looking at the f values generated by anova2
f = anova2(melb_data$Price~melb_data$YearBuilt+melb_data$Car+melb_data$Landsize,melb_data,na.action="omit")[,4]
f
#>melb_data$YearBuilt       melb_data$Car  melb_data$Landsize           Residuals 
#>         1051.06980           892.44127            26.89161                  NA 
```

## More Information
To see more information about these functions, please run
``` r
?lm2
?anova2
```

To see the tutorial and comparision against the original functions, please run
``` r
browseVignettes("HW3")
```

## Contact
If you find any issue or a bug, please email 'eshao@umich.edu' with a minimal reproducible example of this particular issue or bug.
Footer
© 2022 GitHub, Inc.
Footer navigation
Terms
Privacy
Security
Status
Docs
Contact GitHub
Pricing
API
Training
Blog
About
