---
title: "tutorial"
output: rmarkdown::html_vignette
description: >
  This vingette describes how to use 'lm2()' and 'anova2' and what kind of 
  parameters they accepts and the values they return. Additionally, this 
  vingette will give examples of the usuage of 'lm2()' and 'anova2()' and 
  compare 'lm2()' and 'anova2()' against 'lm()' and 'anova()'.
vignette: >
  %\VignetteIndexEntry{HW3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(HW3)
options(max.print=30)
```


## Overview
This vignette will give an introduction of 'lm2' and 'anova2'. It will describe
'lm2' and 'anova2', and give wide examples of they might be used.
It will also compare 'lm2' and 'anova2' against 'lm' and 'anova' respectively. 

Additionally, this vingette will briefly go over on how to load "melb_data.csv",
a sample dataset, which we will use for vignette.

## Loading the melbourne housing dataset, so we can test our package.
```{r setup}
data <- read.csv("C:/Users/s-edw/Documents/HW3/data/melb_data.csv")
```



This package contains two function:
* 'lm2': Mimics the 'lm' function
* 'anova2': Mimics the 'anova' function



## 'lm2()': Fits a linear regression model and performs basic hypothesis testing


To use the function 'lm2':
lm2 is function that fits a linear regression model on a data according to 
the formula provided.

'lm2()' accepts the following parameters:
* 'formula': A framework for how should the linear regression model be given.
  ex: y~x
* 'data': A matrix of (nxp) whose data will be used to form the model.
* 'na.action': How will the missing values be handled. It is defauled to "omit" value.

'lm2()' returns the following values:
A list containing coefficient matrix, residuals, sigma, r.squared, adj.r.squared,
cov.unscaled, fstatistic, var_cov, SSE, SSR, SSY, x, and y.

These values in the list are designed to be same as the ones provided by summary(lm)
and help 'anova2' perform analysis of variance.


** Simple usage of 'lm2()' ~ simple linear regression
```{r lm2-SLR}
output = lm2(data$Price~data$Landsize,data)
output
```
** We can chose not to add the intercept to the model by adding -1 in the 
** formula parameter like this
```{r lm2- no intercept}
output = lm2(data$Price~-1+data$Landsize,data)
output
```

** Other than simple linear regression model, we can use 'lm2' to create 
** multiple linear regression model with the use of '+'
```{r lm2-MLR}
output = lm2(data$Price~data$Landsize+data$YearBuilt,data)
output

```


** We can opt to add interaction terms to the formula parameter in 'lm2()'
** by adding '*'
```{r lm2-interaction}
output = lm2(data$Price~data$Landsize+data$YearBuilt+data$Bedroom2*data$Rooms,data)
output
```

** 'lm2' can set up reference cell coding scheme or cell means coding scheme to help model categorical variables
** by using 'factor()'
```{r lm2-categorical variables}
output = lm2(data$Price~factor(data$Rooms),data)
output

output = lm2(data$Price~-1+factor(data$Rooms),data)
output

```



** Lastly, we can determine how the 'lm2()" will handle the missing values in the
** data.
** If na.action is fail, the function will return the data
** If the na.action is omit, the function will omit rows ith missing values
** Otherwise, it will proceed normally.
```{r lm2- na.action}
output = lm2(data$Price~data$Landsize,data,na.action='omit')
output

output = lm2(data$Price~data$Landsize,data,na.action='fail')
output

```


## 'anova2()': Performs analysis of variance on fitted linear regression model

To use the function 'anova2':
'anova2' is function that performs analysis of variance on fitted linear 
regression model given by 'lm2()'. 

'anova2()' accepts the following parameters:
* 'formula': A framework for how should the linear regression model be given.
  ex: y~x
* 'data': A matrix of (nxp) whose data will be used to form the model.
* 'na.action': How will the missing values be handled. It is defauled to "omit" value.

'anova2()' returns the following values:
A matrix that contains the df, sum of squares, mean sum of squares, F statistic, and
p value for each coefficent and the residuals.

** Simple example of 'anova2()' ~ simple linear regression model
```{r anova2-SLR}
output = anova2(data$Price~data$Landsize,data)
output
```

** We can chose not to add the intercept to the 'model'anova2()' by adding -1 in the 
** formula parameter like this. This will make 'anova2()' perform analysis of 
** variance on a model without intercept.
```{r}
output = anova2(data$Price~-1+data$Landsize,data)
output

```

** Other than simple linear regression model, 'anova2()' can perform analysis of variance
** on multiple linear regression model by using '+' in the formula parameter.
```{r anova2-MLR}
output = anova2(data$Price~data$Landsize+data$YearBuilt,data)
output

```



** We can opt to add interaction terms to the formula parameter in 'anova2()'
** by adding '*'. 'anova2()' can perform analysis of variance on models with
** interaction terms.
```{r anova2-Interaction}
output = anova2(data$Price~data$Landsize+data$YearBuilt+data$Bedroom2*data$Rooms,data)
output
```
** 'anova2' can perform analysis of variance on models using reference cell coding scheme
** or cell means coding scheme
** by using 'factor()'.
```{r anova2-Categorical variables}
output = anova2(data$Price~factor(data$Rooms),data)
output

output = anova2(data$Price~-1+factor(data$Rooms),data)
output
```


** Lastly, we can determine how 'anova2' will handle the missing values
** by setting the na.action parameter.
** If na.action is fail, the funtion will return the data
** If the na.action is omit, the function will omit rows ith missing values
** Otherwise, it will proceed normally.
```{r}
output = anova2(data$Price~data$Landsize,data,na.action='omit')
output

output = anova2(data$Price~data$Landsize,data,na.action='fail')
output

```


### Performance Testing~(lm2 vs. lm)
```{r}
lm2_output = lm2(data$Price~data$Propertycount+data$YearBuilt+data$Bathroom*data$Bedroom2,data,na.action = "omit")
lm_output = summary(lm(data$Price~data$Propertycount+data$YearBuilt+data$Bathroom*data$Bedroom2,data,na.action=na.omit))

```


** Compare residuals
```{r residual comparision}
all.equal(lm2_output$residuals, as.vector(lm_output$residuals))
bench::mark(lm2_output$residuals, as.vector(lm_output$residuals))
```

** Compare sigma
```{r sigma comparison}
all.equal(lm2_output$sigma, lm_output$sigma,) 
bench::mark(lm2_output$sigma, lm_output$sigma)

```

** Compare coefficients
```{r coeff comparision}
all.equal(lm2_output$coefficients, lm_output$coefficients) 
bench::mark(lm2_output$coefficients, lm_output$coefficients)

```

** Compare R Squared
```{r R comparision}
all.equal(lm2_output$r.squared, lm_output$r.squared) 
bench::mark(lm2_output$r.squared, lm_output$r.squared)
```

** Compare Adjusted R Squared
```{r adj R comparison}
all.equal(lm2_output$adj.r.squared, lm_output$adj.r.squared) 
bench::mark(lm2_output$adj.r.squared, lm_output$adj.r.squared)
```
** Compare Variance Covariance Matrix
```{r vcov comparision}
all.equal(lm2_output$var_cov, vcov(lm_output)) 
bench::mark(lm2_output$var_cov, vcov(lm_output))
```
** Compare Covariance Unscaled
```{r cov comparision}
all.equal(lm2_output$cov.unscaled, lm_output$cov.unscaled) 
bench::mark(lm2_output$cov.unscaled, lm_output$cov.unscaled)
```
** Compare F Statistic
```{r F comparision}
all.equal(as.vector(lm2_output$fstatistic), as.vector(lm_output$fstatistic)) 
bench::mark(as.vector(lm2_output$fstatistic), as.vector(lm_output$fstatistic))
```


### Performance Testing~(anova2 vs. anova)
```{r}
anova2_output = anova2(data$Price~data$Propertycount+data$YearBuilt+data$Bathroom*data$Bedroom2,data,na.action = "omit")
anova_output = anova(lm(data$Price~data$Propertycount+data$YearBuilt+data$Bathroom*data$Bedroom2,data,na.action=na.omit))
```


** Compare Degrees of Freedom
```{r DF comparision}
all.equal(unname(anova2_output[,1]), unname(anova_output$Df))
bench::mark(unname(anova2_output[,1]), unname(anova_output$Df))
```

** Compare Sum of Squares (Sequential)
```{r SS comparision}
all.equal(unname(anova2_output[,2]), unname(anova_output$"Sum Sq"))
bench::mark(unname(anova2_output[,2]), unname(anova_output$"Sum Sq"))
```

** Compare Mean Sum of Squares
```{r MSE comparison}
all.equal(unname(anova2_output[,3]), unname(anova_output$"Mean Sq"))
bench::mark(unname(anova2_output[,3]), unname(anova_output$"Mean Sq"))

```


** Compare F Statistics
```{r F comparision}
all.equal(unname(anova2_output[,4]), unname(anova_output$"F value"))
bench::mark(unname(anova2_output[,4]), unname(anova_output$"F value"))
```


** Compare P values
```{r p value comparison}
all.equal(unname(anova2_output[,5]), unname(anova_output$"Pr(>F)"))
bench::mark(unname(anova2_output[,5]), unname(anova_output$"Pr(>F)"))
```

