---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HW3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(HW3)
```


## Loading the melbourne housing dataset, so we can test our package.
```{r setup}
data <- read.csv("C:/Users/s-edw/Documents/HW3/data/melb_data.csv")
```

To use the function 'lm2':
lm2 is function that fits a linear regression model on a data according to 
the formula provided.



```{r}


```

To use the function 'anova2':
```{r}

```

### Comparison(lm2 vs. lm)
```{r}
lm2_output = lm2(data$Price~data$Propertycount+data$YearBuilt+data$Bathroom*data$Bedroom2,data,na.action = "omit",intercept = TRUE)
lm_output = summary(lm(data$Price~data$Propertycount+data$YearBuilt+data$Bathroom*data$Bedroom2,data,na.action=na.omit))

```


** Compare residuals
```{r}
all.equal(lm2_output$residuals, as.vector(lm_output$residuals))
bench::mark(lm2_output$residuals, as.vector(lm_output$residuals))
```

** Compare sigma
```{r}
all.equal(lm2_output$sigma, lm_output$sigma,) 
bench::mark(lm2_output$sigma, lm_output$sigma)

```

** Compare coefficients
```{r}
all.equal(lm2_output$coefficients, lm_output$coefficients) 
bench::mark(lm2_output$coefficients, lm_output$coefficients)

```

** Compare R Squared
```{r}
all.equal(lm2_output$r.squared, lm_output$r.squared) 
bench::mark(lm2_output$r.squared, lm_output$r.squared)
```

** Compare Adjusted R Squared
```{r}
all.equal(lm2_output$adj.r.squared, lm_output$adj.r.squared) 
bench::mark(lm2_output$adj.r.squared, lm_output$adj.r.squared)
```
** Compare Variance Covariance Matrix
```{r}
all.equal(lm2_output$var_cov, vcov(lm_output)) 
bench::mark(lm2_output$var_cov, vcov(lm_output))
```
** Compare Covariance Unscaled
```{r}
all.equal(lm2_output$cov.unscaled, lm_output$cov.unscaled) 
bench::mark(lm2_output$cov.unscaled, lm_output$cov.unscaled)
```
** Compare F Statistic
```{r}
all.equal(as.vector(lm2_output$fstatistic), as.vector(lm_output$fstatistic)) 
bench::mark(as.vector(lm2_output$fstatistic), as.vector(lm_output$fstatistic))
```


### Comparison(anova2 vs. anova)
```{r}
anova2_output = anova2(data$Price~data$Propertycount+data$YearBuilt+data$Bathroom*data$Bedroom2,data,na.action = "omit",intercept = TRUE)
anova_output = anova(lm(data$Price~data$Propertycount+data$YearBuilt+data$Bathroom*data$Bedroom2,data,na.action=na.omit))
```


```{r}

```



